\documentclass[11pt,a4paper]{moderncv}
\moderncvtheme[blue]{classic} 
\usepackage[utf8]{inputenc}  %Windows 
%\usepackage[scale=0.975]{geometry}
\usepackage[top=0.5cm, bottom=0.5cm, left=0.5cm, right=0.5cm]{geometry}
\usepackage{graphicx}
\firstname{Swapnil}
\familyname{Das}
\title{Sophomore B.Tech student}         
\address{SD-18, Kumaon House}{IIT Delhi, New Delhi, 110016}
\mobile{+91 7065158520}
%\phone{(000) 111 1112}
%\fax{(000) 111 1113}
\homepage{http://www.cse.iitd.ac.in/ \textasciitilde cs1150263/}
%\email{cs1150263@iitd.ac.in} 
\email{dasswapnil96@gmail.com} 
%\fax{Votre Fax}                      
%\extrainfo{}
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}                        
\begin{document}
\maketitle
\section{Academic Details}
\cventry{2015--2019}{Bachelor Of Technology In Computer Science Engineering}{\newline Indian Institute of Technology Delhi}{}{\textit{CPI -- 8.588}}{}
\cventry{2015}{CBSE AISSCE}{Hope Hall Foundation School, Delhi}{}{\textit{Percentage -- 95.8\%}}{}
\cventry{2013}{CBSE AISSE}{Jawahar Navodaya Vidyalaya, Assam}{}{\textit{CPI -- 10}}{} 

\section{Relevant Courses}
\cvline{Computer Science}{Data Structures and Algorithms, Discrete Mathematics, Digital Logic and System Design, Introduction to Computer Science, Programming Languages*, Computer Architecture*, Design Practices*.}
\cvline{Mathematics}{Probability and Stochastic Processes, Calculus, Linear
Algebra and Differential Equations.}
\cvline{Electrical}{Introduction To Electrical Engineering, Signals \& Systems*.}
\cvline{Online}{Introduction to Computer Networking(Stanford), Parallel Programming(EPFL), CS50(Harvard).}
\cvline{}{\scriptsize *Courses to de done by summer 2017.}

%\section{Projects}
\section{Course Projects}
\cventry{August - Present}{Mobile Phone Tracking}{Under Prof. Amitabha Bagchi}{CSE, IIT Delhi}{}{{\begin{itemize}\item{Developed a multithreaded model in Java to replicate real life mobile tracking  in a area.}
\item{Analysed the Two-way-Radio system of connection.}\end{itemize}}}
\cventry{July - August, 2016}{Multithreading Stock Exchange}{Under Prof. Amitabha Bagchi}{CSE, IIT Delhi}{}{{\begin{itemize}
\item{Implemented a mutithreaded model of stock exchange and profit is calculated using 3 different threads.}
\item{Data from a file was processed but in real time using threads.}\end{itemize}}}
\section{Independent Projects} 
\cventry{May - July, 2016}{Peer-to-peer networking}{Python}{Sockets}{ Link - https://github.com/swapnil96/P2P-chat}{
{\begin{itemize}
\item{Created a P2P service where multiple clients log into a central server and eventually connect to other clients.}
\item{Server authenticates and manages multiple chat sessions. }
\item{Analysed crowding and high bandwidth consumption in network by connecting 8 systems simultaneously.}\end{itemize}}}
\cventry{April - May, 2016}{Applications of Brute Force Technique}{Python}{Link - https://github.com/swapnil96/Brute-Force}{}{{\begin{itemize}
\item{Implemented Backtracking alogrithm to solve Peg-soltaire, Sudoku solver, Magic-square finder.}
\item{Measured the limit of brute force on a system of 2.4Ghz Intel i7 quad core processor.}\end{itemize}}}
%\cventry{March - July, 2016}{Personal Website}{HTML5}{CSS3, Javascript}{}{{\begin{itemize}
%\item{Created my own website using Bootstrap framework and jquery.}\end{itemize}}}
%\cventry{Jan - Feb, 2016}{GUI of Depth First Search}{Python}{Tkinter.Link - https://github.com/swapnil96/Miscellaneous/blob/master/maze.py}{}{Implemented Python Tkinter module to make a maze where a solution is found from start to end using DFS.}

\section{Technical Skills}
\cvline{Languages}{Python, Java, C++, C, VHDL, HTML, CSS3, MySql, Javascript}
\cvline{Frameworks}{Bootstrap, Django, JQuery, Socket, TKinter, Web2Py}
\cvline{Softwares}{GIT, Xilinx ISE suite, Autodesk Inventor, Android Studio, Visual Studio, \LaTeX, MS office}


\section{Scholastic Achievements}
\cvline{2015}{Secured \textbf{All India Rank 2666}(category-\textbf{28}) in JEE-Advance, 2015 among \textbf{0.15 Million} candidates.}
\cvline{2015}{Secured \textbf{All India Rank 1728}(category-\textbf{17}) in JEE-Main 2015 among \textbf{1.4 million} candidates.}
\cvline{2015}{Awarded Scholarship of Merit by CBSE for being in \textbf{top 25 among 1 Million} in AISSCE.}
%\cvline{2014}{Attended Science Camp at Kolkata(India) organized by \textbf{IISc and IISER}.}
\cvline{2014}{Selected as \textbf{(KVPY)} scholar under 'Kishore Vaigyanik Protsahan Yojana' given to top 1\% conducted by \textbf{IISc} Bangalore and \textbf{Govt. of India.}}
\cvline{2013}{Awarded Scholarship of Merit by CBSE for being in \textbf{top 27 among 1.3 Million} in AISSE.}
%\cvline{2013}{Qualified to appear in \textbf{Indian National Mathematics Olympiad(INMO)} conducted by \textbf{Homi Bhabha Centre for Science Education(HBCSE)}.}
\cvline{2013}{Selected as Dakshana scholar for qualifying in GDST conducted by \textbf{HRD ministry Govt. of India}.}
\cvline{2012}{Qualified \textbf{Regional Mathematics Olympiad(RMO)} and appeared in \textbf{Indian National Mathematics Olympiad(INMO)} conducted by \textbf{Homi Bhabha Centre for Science Education(HBCSE)}.}

\section{Extra Curricular Achievements}
\subsection{Programming Contest}
\cvline{Jan 2016}{\textbf{Microsoft Code.Fun.Do Hakathon} - Runners up. Created a game in Visual Studio using C\#}
\cvline{July 2016}{\textbf{Microsoft Finalist Forum} - Participated online and completed 1st round.}
\cvline{April 2016}{Qualified Google Code Jam qualifying round.}
%\cvitem{Codeforces}{
%Handle: \textbf{dasswapnil96}, {}
%Max Rating: 1410}
%\cvitem{Codechef}{
%Handle: \textbf{dasswapnil96}, {}
%Rank: 3109 - Global, 2335 - India}
\subsection{Others}
\cvline{2012}{Regional Badminton Player from JNV under Shillong Region.}
\cvline{2002 - 2009}{Completed a 7 year course in Fine – Arts.}

\section{Position of Responsibility}
\cvline{2016-17}{Website executive of eDC team, IIT Delhi.}
\cvline{2016-17}{Activity Head in TRYST(Annual technical festival) 2017 of IIT Delhi.}
%\cvline{2016-17}{Volunteer in Training and placement cell, IIT Delhi.}

%\section{References}
%\cventry{}{Rupam Barman}{IIT Guwahati, Assam, rupam@iitg.ernet.in.}{}
%{\newline Associate Professor in Mathmetics department IIT Guwahati.}{}
\end{document}
